# Part B Q3
# Clear Memory & Set Data File Path

Put the path of the customer_churn file folder as argument for setwd("customer_churn file folder path")

```{r}
rm(list = ls(all.names = TRUE)); gc();
setwd("D:/uOttawa/First Semister/Fundamentals and Applied Data Science/Assignment 1/Assignment 1")
```
# Load customer_churn.csv file Data in DataFrame

Load customer_churn.csv file Data in DataFrame.

```{r}
# Specify the path to your CSV file
csv_file_path <- "customer_churn.csv"
# Load the data from the CSV file into a data frame
customer_churn_data <- read.csv(csv_file_path)
```
# Explore customer_churn data

```{r}
head(customer_churn_data)
```

```{r}
str(customer_churn_data)
```
# Build Total Revenue Cube
that it's dimensions are
• offer type            (Offer)
• internet service type (Internet.Type)
• contract duration     (Contract)
• customer Status       (Customer.Status)
so we can apply cube operations regarding those attributes perform adhoc quires.

```{r}
Total.Revenue_cube <- 
  tapply(customer_churn_data$Total.Revenue, 
         customer_churn_data[,c("Offer", "Internet.Type", "Contract", "Customer.Status")], 
         FUN=function(x){return(sum(x))})
```
# a)
## ROLLUP Total Revenue Cube & Collapse Customer Status Dimension
to aggregate revenue across different customer status in the cube

```{r}
Summarized_Total.Revenue_cube <-
  apply(Total.Revenue_cube, c("Offer", "Internet.Type", "Contract"),
      FUN=function(x) {return(sum(x, na.rm=TRUE))})
```
## Show The total revenue contribution
from a Two Year contract for each Offer by internet type by Cube Slice operation

```{r}
Total.Rev.2yr_cont.per.off <- Summarized_Total.Revenue_cube[,,"Two Year"]
print(Total.Rev.2yr_cont.per.off)
```
# b)
## Calculate Total Revenue From Offer B customers

```{r}
Offer.B_Total.Revenue <- sum(Summarized_Total.Revenue_cube["Offer B",,])
```
## Calculate Total Revenue From Offer B churned customers 
that accepted Month-to-Month Contract for Cable internet service type

```{r}
Offer.B_churn_mon.to.mon_cable_Total.Revenue <- sum(Total.Revenue_cube["Offer B","Cable","Month-to-Month","Churned"])
```
## Calculate Total Revenue Precentage (for Offer B)
contributed by churned customers that accepted a Month-to-Month contract for Cable service

```{r}
total_rev_precent = Offer.B_churn_mon.to.mon_cable_Total.Revenue / Offer.B_Total.Revenue * 100
print(paste(total_rev_precent,"%"))
```